---
title: "Usecases for agroenv"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{aa-usecase}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(agroenv)

```

## Get information on climate stations or grid cells around a given geographical location

* world: agroenv is only a wrapper around the nasapower package [open].
* Europe: agri4cast gridded data is used [open].
* France: network from Meteo-France stations and gridded data from the SAFRAN model [closed]. Related climate data are not distributed here but if you are an authorized user, the agroenv package helps read and format these datasets.

```{r grid}
location <- data.frame(lat=43.5279, lon=1.5009)

get_station(location$lat, location$lon, network="meteofrance", n=1)

get_station(location$lat, location$lon, network="safran", n=1)
```

## Get climate data in the same format from various sources

```{r data_nasapower}

# get_climate_nasapower(lat=location$lat, lon=location$lon, year=2003)
```

```{r data_safran, eval=FALSE}
path_safran <- "~/Documents/INRA/Database/db_safran"

get_climate_safran(lat=location$lat, lon=location$lon, year=2003, path=path_safran)

```

## Get soil data

* Europe : European Soil Database (ESDB), derived [data](http://esdac.jrc.ec.europa.eu/content/esdb-derived-data) [@Hiederer2013] [open]. Related soil data are not distributed with this package.

* france : INRAE UMR INFOSOL, *Carte de la Réserve Utile en eau* [doi](http://dx.doi.org/10.15454/JPB9RB) [@LeBas2018] [open]

```{r data_esdb, eval=FALSE}
path_esdb <- "~/Documents/INRA/Database/db_esdb"

load(paste0(path_esdb, "/data_soil.rda"))

get_soil_esdb(lat=location$lat, lon=location$lon, data=data_soil)

```


