---
title: "Usecases for agroenv"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{aa-usecase}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(tidyverse)
library(agroenv)

```

## Get information on climate stations or grid cells around a given geographical location

* world: agroenv is only a wrapper around the nasapower package [open].
* Europe: agri4cast gridded data is used [open].
* France: network from Meteo-France stations and gridded data from the SAFRAN model [closed]. Related climate data are not distributed here but if you are an authorized user, the agroenv package helps read and format these datasets.

```{r grid, eval=FALSE}
location <- data.frame(lat=43.5279, lon=1.5009)

get_station(location$lat, location$lon, network="meteofrance", n=1)

get_station(location$lat, location$lon, network="safran", n=1)
```

## Get climate data in the same format from various sources

```{r data_nasapower, eval=FALSE}
location <- data.frame(lat=43.5279, lon=1.5009)

get_climate_nasapower(lat=location$lat, lon=location$lon, year=2003)

```

```{r data_safran, eval=FALSE}
location <- data.frame(lat=43.5279, lon=1.5009)

path_safran <- "~/Documents/INRA/Database/db_safran"

get_climate_safran(lat=location$lat, lon=location$lon, year=2003, path=path_safran)

```

```{r data_meteofrance, eval=FALSE}
# https://meteo.data.gouv.fr/datasets/6569b51ae64326786e4e8e1a
library(agroenv)

dep = 31
loc = c(lat = 43.489374, lon = 1.514382)
path = "https://object.files.data.gouv.fr/meteofrance/data/synchro_ftp/BASE/QUOT"

file = glue::glue("{path}/Q_{dep}_latest-2024-2025_RR-T-Vent.csv.gz")

table_climate <- read_delim(file) |> mutate(date = ymd(AAAAMMJJ))

table_station <- get_station(loc["lat"], loc["lon"], n = 10) |> 
  distinct() |> select(NUM_POSTE = station_id, distance) 

table_climate |> 
  inner_join(table_station) |> 
  group_by(NUM_POSTE, NOM_USUEL) |> 
  filter(between(date, today() - 30, today())) |> 
  summarise(RR = sum(RR), distance = unique(distance)) |> arrange(distance)

```

## Get soil data

* Europe : European Soil Database (ESDB), derived [data](http://esdac.jrc.ec.europa.eu/content/esdb-derived-data) [@Hiederer2013] [open]. Related soil data are not distributed with this package.

* france : INRAE UMR INFOSOL, *Carte de la Réserve Utile en eau* [doi](http://dx.doi.org/10.15454/JPB9RB) [@LeBas2018] [open]

```{r data_esdb, eval=FALSE}
path_esdb <- "~/Documents/INRA/Database/db_esdb"

location <- data.frame(lat=43.5279, lon=1.5009)

load(paste0(path_esdb, "/data_soil.rda"))

get_soil_esdb(lat=location$lat, lon=location$lon, data=data_soil)

# get_param_soil(lat=location$lat, lon=location$lon, data=data_soil)

```


